Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-24 paper/paper.tex
add non-final cases description

We can now faithfully describe the state transition function @step@,
which when given a machine state, determines its successor state.

@@

As shown and previously discussed, we examine the only two cases which the state may be.

>>>>

We can now faithfully describe the state transition function @step@,
which when given a machine state, determines its successor state.
The function @step@ is a partial function that only handles non-final states,
which must have a successor; the final case of a state is handled by funciton
@drive@, which will be mentioned in the next section.

@@

As shown and previously discussed, we examine the only two non-final cases which the state
may be.
